\ \\ \LARGE\bf Rolling Horizon methods for Games with Continuous States and Actions

### 2014-04-07 lpaper/lunarcont.tex
Experiments done, a bit more effort needed to cleanup

  \centering
        \begin{subfigure}{0.49\textwidth}
                \centering
                \includegraphics[width=1.0\textwidth]{./lunarexps/sample-crop.pdf}
                \caption{Best value for each tick EVO-P could find. }
                \label{fig:sample}
        \end{subfigure}  
        \begin{subfigure}{0.49\textwidth}
                \centering
                \includegraphics[width=1.0\textwidth]{./lunarexps/sample-detail-crop.pdf}
                \caption{Detail of Figure \ref{fig:sample}, when the ship is closer to landing.}
                \label{fig:sample-detail}

@@

         \caption{Sample run for EVO-P. Best fitness discovered at each tick is shown. Notice the big ``bump'' in fitness when the ship gets close to the landing pad}
         \label{fig:samples}

>>>>

\begin{table}
	\begin{tabular}{lrrrr}
\hline
 Map Name   &   Success Mean &   Success CI &   Ticks Mean &   Tick CI \\
\hline
 map2       &            1   &     0        &       2925.9 &   184.437 \\
 map1-tall  &            1   &     0        &       2733   &   159.34  \\
 map1-easy  &            1   &     0        &       2293   &   123.917 \\
 map1-wall  &            0.9 &     0.226216 &       2421.6 &   682.893 \\
\hline
\end{tabular}
\end{table}

% \begin{figure*}[ht]
%   %\centering

%   \centering
%         \begin{subfigure}{0.49\textwidth}
%                 \centering
%                 \includegraphics[width=1.0\textwidth]{./lunarexps/sample-crop.pdf}
%                 \caption{Best value for each tick EVO-P could find. }
%                 \label{fig:sample}
%         \end{subfigure}  
%         \begin{subfigure}{0.49\textwidth}
%                 \centering
%                 \includegraphics[width=1.0\textwidth]{./lunarexps/sample-detail-crop.pdf}
%                 \caption{Detail of Figure \ref{fig:sample}, when the ship is closer to landing.}
%                 \label{fig:sample-detail}

%         \end{subfigure}

%          \caption{Sample run for EVO-P. Best fitness discovered at each tick is shown. Notice the big ``bump'' in fitness when the ship gets close to the landing pad}
%          \label{fig:samples}

% \end{figure*}

\begin{figure*}[ht]
  \centering

  \centering
        \begin{subfigure}{0.49\textwidth}
                \centering
                \includegraphics[width=1.0\textwidth]{./graphics/map2.pdf}
                \caption{Map. }
                \label{fig:map2}
        \end{subfigure}  
        \begin{subfigure}{0.49\textwidth}
                \centering
                \includegraphics[width=1.0\textwidth]{./graphics/map1-easy.pdf}
                \caption{sdfdf}
                \label{fig:map1-easy}

        \end{subfigure}
\\
        \begin{subfigure}{0.49\textwidth}
                \centering
                \includegraphics[width=1.0\textwidth]{./graphics/map1-tall.pdf}
                \caption{Detail of Figure \ref{fig:sample}, when the ship is closer to landing.}
                \label{fig:map1-tall}\end{subfigure}\begin{subfigure}{0.49\textwidth}
                \centering
                \includegraphics[width=1.0\textwidth]{./graphics/map1-wall.pdf}
                \caption{Detail of Figure \ref{fig:sample}, when the ship is closer to landing.}
                \label{fig:map-wall}

@@

         \caption{Sample run for EVO-P. Best fitness discovered at each tick is shown. Notice the big ``bump'' in fitness when the ship gets close to the landing pad}
         \label{fig:maps}
